---
output:
  html_document:
    theme: flatly
    toc: true
---

```{r config, echo = FALSE}
library(knitr)
opts_chunk$set(
  echo = FALSE
)
```

```{r parallel-reports, engine = "dot"}
digraph {
  fontname = helvetica;
  fontsize = 20;
  rankdir = LR;
  size = "20!";

  node[fontname = helvetica];
  node[fontsize = 10; size = 20; shape = "none"];

  label = "Parallel reports";
  labelloc = top;

  {setup, models, plots} -> report[arrowhead = "none"; tailport = "e"; headport = "w"];

  setup[label = "setup.R"];
  models[label = "models.R"];
  plots[label = "plots.R"];

  report[label = "report.Rmd"];
}
```

**Parallel reports** are dynamic documents where the text and the code are purposefully disentangled.

## Description

* **Intent**. Write exploratory reports that evolve into final reports.
* **Scenario**. You want to have a completely dynamic report but your
  development time is impaired or you otherwise have a hard time writing complicated R code in knitr chunks.
* **Solution**. Write R code in normal .R files and load it into
  dynamic reports using the `knitr::read_chunk` function.

## Motivations

1. Interactive development of reports is hard to do right, in a way that
   encourages you to write the best code with the greatest payoffs down the road.
2. There will always be more code than room on the final report or
   presentation.
3. It's sometimes hard to reuse code used for literate documentation.

## Introducing read_chunk

The solution I have discovered is to write normal .R scripts and use the knitr function `read_chunk` to load them into my dynamic documents:

    # report.Rmd

    ```{r}
    library(knitr)
    read_chunk("report.R")
    ```

    ```{r report}
    ```

`read_chunk` looks at .R scripts and loads chunk by label looking for special comments like this:

    # ---- label
    # ... normal R code here

Then, these chunks can be used in Rmd reports:

    ```{r label}
    ```

Note that the chunks are empty, and take up very little space in the report. knitr fills in the content of the chunks based on the label when it is compiled.

## Principles of chunk files

The point of separating chunk files from the .Rmd report is that sometimes you want to be able to jump in and run all of the code easily, move things around, and refactor at will. Make sure you can always open up any of the chunk files and run them without issue in an empty environment.

## Caveats

- Parallel reports is basically undoing some of what is great about
  interleaving documentation and code. Use only if you find it difficult to be productive on long documents.
- There is some inevitable duplication. Keep chunk labels as intuitive as you
  can.
